---
title: "Assignment_4_1821_twu38"
author: "Tianqi Wu"
date: "12/6/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
```

```{r}
library(dplyr)
library(recommenderlab)  
library(reshape2) 
set.seed(1821)
```

```{r}
# ratings data
# use colClasses = 'NULL' to skip columns
ratings = read.csv('ratings.dat', sep = ':', 
    colClasses = c('integer', 'NULL'), header = FALSE)
colnames(ratings) = c('UserID', 'MovieID', 'Rating', 'Timestamp')
#dim(ratings) # 1000209-by-4
#ratings[1:4, ]

# movies data
# In movies.dat, some movie names contain single colon (:), so the above 
# method does not work. 

movies = readLines('movies.dat')
movies = strsplit(movies, split = "::", fixed = TRUE, useBytes = TRUE)
movies = matrix(unlist(movies), ncol = 3, byrow = TRUE)
movies = data.frame(movies, stringsAsFactors = FALSE)
colnames(movies) = c('MovieID', 'Title', 'Genres')
movies$MovieID = as.integer(movies$MovieID)
```

```{r}
ratings$Timestamp = NULL;
colnames(ratings) = c('user', 'movie', 'rating')
set.seed(1821)
train.id = sample(nrow(ratings), floor(nrow(ratings)) * 0.6)
train = ratings[train.id, ]
#head(train)

test = ratings[-train.id, ]
test.id = sample(nrow(test), floor(nrow(test)) * 0.5)
test = test[test.id, ]
#head(test)

label = test[c('user', 'rating')]
test$rating = NULL
#head(label)
#head(test)
```

```{r}
R = acast(train, user ~ movie)
R = as(R, 'realRatingMatrix')
R_m = normalize(R)
head(getRatingMatrix(R_m))
```

```{r}
# visualize
#image(R, main = "Raw Ratings")
#image(R_m, main = "Normalized Ratings")

#recommenderRegistry$get_entries(dataType = "realRatingMatrix")
rec = Recommender(R, method = 'UBCF',
    parameter = list(normalize = 'Z-score', method = 'Cosine', nn = 5)
    )

#print(rec)
#names(getModel(rec))

recom = predict(rec, R, type = 'ratings')  # predict ratings. This may be slow.
rec_list = as(recom, 'list')  # each element are ratings of that user
```

```{r}
test$rating = NA

# For all lines in test file, one by one
for (u in 1:nrow(test)){

    # Read userid and movieid from columns 2 and 3 of test data
    userid = as.character(test$user[u])
    movieid = as.character(test$movie[u])
    
    rating = rec_list[[userid]][movieid]
    # 2.5 may be too arbitrary
    test$rating[u] = ifelse(is.na(rating), 2.5, rating)
}
```

```{r}
rec2 = Recommender(R, method = 'IBCF')

recom2 = predict(rec2, R, type = 'ratings')  # predict ratings. This may be slow.
rec_list2 = as(recom2, 'list')  # each element are ratings of that user
```

```{r}
test2 = test
test2$rating = NA

# For all lines in test file, one by one
for (u in 1:nrow(test2)){

    # Read userid and movieid from columns 2 and 3 of test data
    userid = as.character(test2$user[u])
    movieid = as.character(test2$movie[u])
    
    rating = rec_list2[[userid]][movieid]
    # 2.5 may be too arbitrary
    test2$rating[u] = ifelse(is.na(rating), 2.5, rating)
}
```

Both models use the package recommenderlab from R to learn the recommender.The first model uses method 'UBCF'(User Based Collaborative Filtering) with parameters: normalize = 'Z-score', method = 'Cosine', nn = 5. The RMSE is:
```{r,include=TRUE}
RMSE(test$rating,ratings[-train.id,][test.id,]$rating)
```

The second model uses method 'IBCF'(Item Based Collaborative Filtering) with default parametes. The RMSE is:
```{r,include=TRUE}
RMSE(test2$rating,ratings[-train.id,][test.id,]$rating)
```

Overall, the script may take around half an hour to run. The computer system is Macbook Pro 3.1GHz, 8GB memory.